---
title: "hmk_04"
format: gfm
editor: visual
---
## loading of the tidyverse library
```{r, message=FALSE}
library(tidyverse)
```
## step1: reading of data file hmk directory
## step 2: representation of pvalue in the form of tiles using geom_tile. the x axis represents the gene symbol and its corresponding p value plotted when the cells are differentited into adipocytes
```{r}
experiment <- read_csv(file = "C:/Users/ngogia/Documents/classes_2022/micr_575/hmk/my_data.csv")

glimpse(experiment)
z <- experiment$P.val

plot1 <- ggplot(experiment) + 
  geom_tile(aes(x = Gene.Symbol, y = adipogenesisAvg.log2, fill = z)) +
  scale_fill_gradient(low="blue", high="red")

print(plot1)


```
## To test whether I could change the shape of the tiles in the data which is described above. 
```{r}
plot2 <- ggplot(experiment) + 
  geom_tile(aes(x = Gene.Symbol, y = adipogenesisAvg.log2, fill = z), 
            width = 0.25 , height = 0.25) + 
  scale_fill_gradient(low="blue", high="red")

print(plot2)


```
## Representation of the above data in form of a violin plot.
```{r}
plot3 <- ggplot(experiment) + 
  geom_violin(aes(x = Gene.Symbol, y = adipogenesisAvg.log2 ),
                color = "green")

print(plot3)

```
## using the geom_histogram to represent the data in the form of a histogram
```{r}
plot4 <- ggplot(experiment) +
  geom_histogram(aes(y = adipogenesisAvg.log2), color = "purple")

print(plot4)
```

